Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-18 paper/main.tex
rephrase long sentences at discussions beginning

% previous studies
Several studies have reported increased hemodynamic activity in the PPA,
attributed to the processing of spatial information, for example, when
participants were watching static pictures of landscapes compared to pictures of
faces or objects \citep[e.g.,][]{epstein1998ppa, epstein1999parahippocampal}.
However, reports regarding the correlates of processing spatial information in
auditory semantic stimulation are less clear \citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we investigated the hemodynamic response to
spatial information using a model-based, mass-univariate approach.
% current study: dissimilar
However, instead of using a conventional set of stimuli, assembled to
specifically and predominantly evoke the processing spatial information, we
employed a naturalistic movie stimulus that was designed for entertainment.

% PPA: intro
In an earlier study, \cite{bartels2004mapping} manually annotated the content
of individual movie frames (color, faces, language, and human bodies) and found
that the expected specialization of functional areas is preserved during movie
watching.
%
In contrast, we aimed to exploit a cinematographic confound in the stimulus
structure, where
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the spatial layout of locations in earlier
shots and later focus more on detailed depictions of people and objects
\citep{brown2012cinematography,
katz1991film, mascelli1998five}.
% hypo
We\todo{following two sentences are confusing imo} hypothesized that due to the complex nature of a naturalistic stimulus,
unrelated factors would be balanced across a large number of events, and make
the bias of spatial information availability in particular events accessible to
convential model-based statistical analysis of BOLD fMRI data.
%
This approach required a detailed description of the occurence of relevant
stimulus features. For both types of naturalistic stimuli used here, a movie
and its audio-description, this annotation revealed the respective number of
incidentally occurring events to be similar to those of a conventional
experimental paradigm used in neuroimaging, for the purpose of localizing
particular regions of interest.

>>>>

% previous studies
Several studies have reported increased hemodynamic activity in the PPA
attributed to the processing of spatial information, for example, when
participants were watching static pictures of landscapes compared to pictures of
faces or objects \citep[e.g.,][]{epstein1998ppa, epstein1999parahippocampal}.
% auditory semantics unclear
However, reports regarding the correlates of processing spatial information in
verbal stimulation are less clear \citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we investigated the hemodynamic response to
spatial information using a model-based, mass-univariate approach.
% current study: dissimilar
However, instead of using a conventional set of stimuli, assembled to
specifically and predominantly evoke the processing of spatial information, we
employed a naturalistic movie stimulus that was designed for entertainment.

% PPA: intro
In an earlier study, \cite{bartels2004mapping} manually annotated the content of
individual movie frames (color, faces, language, and human bodies) and found
that the functional specialization of brain areas is preserved during movie
watching.
%
In contrast, we aimed to exploit a cinematographic confound in the stimulus
structure, where
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the spatial layout of locations in earlier
shots and later focus more on detailed depictions of people and objects
\citep{brown2012cinematography, katz1991film, mascelli1998five}.
% hypo
We hypothesized that due to the complex nature of a naturalistic stimulus,
unrelated factors would be balanced across a large number of events, and make
the bias of spatial information accessible to a convential model-based
statistical analysis of BOLD fMRI data.
% we need a detailed description -> annotation
The current model-driven approach required a detailed annotation of the
occurence of relevant stimulus features.
% event counts ftw
The annotation of both types of naturalistic stimuli, a movie and its
audio-description, revealed the respective number of incidentally occurring
events to be similar to those of a conventional experimental paradigm used to
localize functional regions of interest.
